Blocks of extended ancestry around selected loci in hybrid zones

### 2016-02-28 drafts/hybrid_zone.tex
more comparison figs

@@

\section*{Single-locus behavior}

@@

@@

The diffusion model for lineages predicts that quantities of interest solve sets of coupled partial differential equations (PDE),
which we have written down.
As there are no known analytical solutions to these PDE,
we have constructed numerical solutions (and provide the source code for doing this).
A main role of these solutions in our work has been to verify that theory based on the diffusion model of lineages
matches the simulations.
These solutions easily and quickly provide predictions of joint frequencies at small numbers of loci.
However, due to the high dimensionality of the haplotype problem (spatial position $\times$ time $\times$ endpoints of the haplotype),
numerical solutions for mean haplotype lengths along the genome can be as computationally intensive as simulations
(although are substantially less noisy).
More work could be done to develop more efficient methods of solution,
but it may be better to perform more biologically realistic forwards-time simulations that includes coalescence and drift.
Nonetheless, the PDE approach is easily modified to provide predictions for spatial and temporally inhomogeneous systems --
for instance, across maps of real landscapes.

>>>>

\plr{say what population density in simulation figures}

@@

\subsection*{Comparison of theory and simulation}

The theoretical results described above matched well with our individual-based simulations,
across a large range of parameter values.
This can be seen by comparing
clines in frequency of $A$ ancestry at linked loci,
either unconditional on the identity of the linked selected allele (Figure \ref{sfig:alleleFreq_tau100_comparison}),
or conditional on its identity 
(Figures \ref{sfig:condAlleleFreq_tau80_comparison}, \ref{sfig:condAlleleFreq_tau320_comparison}, and \ref{sfig:condAlleleFreq_tau1280_comparison}).

\subsection*{Single-locus behavior}

@@

\plr{note that when drift starts to kick in for clines (around $\tau=320$) we start to get better power with haplotype lengths}

@@

The diffusion model for lineages predicts that quantities of interest solve sets of coupled partial differential equations (PDE),
which we have written down.
As there are no known analytical solutions to these PDE,
we have constructed numerical solutions (and provide the source code for doing this).
A main role of these solutions in our work has been to verify that theory based on the diffusion model of lineages
matches the simulations.
These solutions easily and quickly provide predictions of joint frequencies at small numbers of loci:
about 1 second to compute predicted clines, as opposed to hours for the full simulation.
However, due to the high dimensionality of the haplotype problem (spatial position $\times$ time $\times$ endpoints of the haplotype),
numerical solutions for mean haplotype lengths along the genome can be as computationally intensive as simulations
(although are substantially less noisy).
More work could be done to develop more efficient methods of solution,
but it may be better to perform more biologically realistic forwards-time simulations that includes coalescence and drift.
Nonetheless, the PDE approach is easily modified to provide predictions for spatial and temporally inhomogeneous systems --
for instance, across maps of real landscapes.
